Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2018-06-10 paper/galsize_paper.tex
Expanded discussion of correl program

For our SDSS galaxy samples, we calculate two-point clustering $\wproj$ using line-of-sight projection of $\pi_{\rm max}=20~\mpc$ using the {\tt correl} program in {\tt UniverseMachine} (Behroozi et al. 2017, in prep). As a function of projected separation, the {\tt correl} code calculates the number of pairs of galaxies, DD, the number of pairs of galaxy-randoms, DR, and the number of random-random pairs, RR. Using the \citet{landy_szalay93} estimator ($DD - 2DR + RR$), we compute the redshift-space correlation function $\xi(\rproj, \pi)$, which is then integrated over $\vert\pi\vert < 20$ Mpc to compute the projected correlation function $\wproj(\rproj)$.  The code uses $10^6$ randoms drawn from the same mask region with uniform volume distribution to compute $DR$, and $RR$ is computed via Monte Carlo integration. Errors are estimated by jackknife resampling, giving us an estimate for the lower bound of samples with volumes $V_{\rm eff}\lesssim 0.3\,{\rm Gpc}^3.$

We measure $\wproj(\rproj)$ separately for large and small subsamples for four different $\mstar$ thresholds: an  $\mstar>10^{9.75}\msun$ sample with $z_{\rm max}=0.0435$ and $N_{\rm gal}=27658;$ an  $\mstar>10^{10.25}\msun$ sample with $z_{\rm max}=0.0663$ and $N_{\rm gal}=48571;$ 
an  $\mstar>10^{10.75}\msun$ sample with $z_{\rm max}=0.1$ and $N_{\rm gal}=52350;$ 
and an  $\mstar>10^{11}\msun$ sample with $z_{\rm max}=0.1$ and $N_{\rm gal}=33578.$ We follow standard practice \citep[e.g.,][]{zehavi_etal11} and throw out all galaxies with $z<z_{\rm min}=0.02;$ we also throw out galaxies with redshift $z \geq z_{\rm max}=0.1$ even in cases where a volume-limited sample would be attainable out to higher redshift.

>>>>

For our SDSS galaxy samples, we calculate two-point clustering $\wproj$ using line-of-sight projection of $\pi_{\rm max}=20~\mpc$ using the {\tt correl} program in {\tt UniverseMachine} (Behroozi et al. 2017, in prep). For two samples of points distributed in redshift space, $\vec{x}_1$ and $\vec{x}_2,$ with $\vec{s}\equiv\vec{x}_2-\vec{x}_1$ and $\vec{l}\equiv0.5(\vec{x}_2+\vec{x}_1),$ the {\tt correl} code program counts the number of pairs of points within a line-of-sight distance $\pi\equiv(\vec{s}\cdot\vec{l})/\vert\vec{l}\vert$ and transverse separation $r_{\rm p}\equiv\sqrt{s^{2} - \pi^{2}}.$ When both sets of points are galaxy data, the resulting pair-counts are denoted by DD; when both sets are random points, RR; cross-counts between data and randoms are denoted by DR. Using the \citet{landy_szalay93} estimator ($DD - 2DR + RR$), we compute the redshift-space correlation function $\xi(\rproj, \pi)$, which is then integrated over $\vert\pi\vert < 20$ Mpc to compute the projected correlation function $\wproj(\rproj)$.  The code uses $10^6$ randoms drawn from the same mask region with uniform volume distribution to compute $DR$, and $RR$ is computed via Monte Carlo integration. Errors are estimated by jackknife resampling, giving us an estimate for the lower bound of samples with volumes $V_{\rm eff}\lesssim 0.3\,{\rm Gpc}^3.$

We measure $\wproj(\rproj)$ separately for large and small subsamples for four different $\mstar$ thresholds: an  $\mstar>10^{9.75}\msun$ sample with $z_{\rm max}=0.0435$ and $N_{\rm gal}=27658;$ an  $\mstar>10^{10.25}\msun$ sample with $z_{\rm max}=0.0663$ and $N_{\rm gal}=48571;$ 
an  $\mstar>10^{10.75}\msun$ sample with $z_{\rm max}=0.1$ and $N_{\rm gal}=52350;$ 
and an  $\mstar>10^{11}\msun$ sample with $z_{\rm max}=0.1$ and $N_{\rm gal}=33578.$ We follow standard practice \citep[e.g.,][]{zehavi_etal11} and throw out all galaxies with $z<z_{\rm min}=0.02$ to minimize lightcone effects; to minimize the effect of redshift evolution we also throw out galaxies with redshift $z \geq z_{\rm max}=0.1,$ including cases where a volume-limited sample would be attainable out to higher redshift.
